Individual Variation in Animal Movement

### 2021-03-24 movement_paper/rudolph_ch2.Rmd
distributions
Removed section went to distributions paper

## Why do we study animal movement and what can it tell us?
   Movement is a fundamental ecological process, critical to an animal's biology and it's interactions with the environment. The study of animal movement tends to focus on four basic mechanistic questions: the why, when, where, and how, and these questions can be answered at the scales of individuals or populations. A general framework for movement ecology that allows to link movement patterns and processes, starts with a focus on movement itself and the individual's internal state, navigation capacity, motion capacity, and responses to external factors [@nathan2008movement]. The overall goal of studying movement seeks to find the linkages between the causes and mechanisms of animal movement, that result in spatiotemporal patterns that feedback to various ecological and evolutionary processes.

## What is the importance of individual variation in animal movement?  
  Although there is variation in animal movement at the individual scale, the general focus has been on understanding the typical movement patterns, built around average measures at population levels. This focus on generality has driven to a lack of frameworks for understanding variation, how it is maintained, and the consequences of this variation across populations, communities, and ecosystems. Although there have been recent calls for incorporating individual variation in movement [@snell2019consequences, @shaw2020causes] we still need to develop theory that explores different types of variation in movement patterns to understand its consequences across these levels. In particular, when considering species interactions, incorporating individual variation becomes essential to understand how positive or negative feedback loops play into the maintenance of variation in movement as individuals respond to external factors in their environment [@shaw2020causes].

@@

>>>>

@@

# Notes on March 17, 2021

So, one of the main questions I have is that I am trying to decipher animal paths yet it seems like most animal movement ecologists are trying to figure out behavioral states out of movement data, which is not my focus. 
Reading the [@langrock2012flexible] paper.
